### 2014-11-01 implementation.tex
implementation

Every generated effect on an object inserts a new row
$(o,e,\mathit{vis},\mathit{txn},\mathit{val})$ into the backing store, where
$o$ and $e$ are object and (unique) effect identifiers, \emph{vis} is the
set of effect identifiers visible to this operation, \emph{txn} is an
optional transaction identifier, and \mathi{val is the value associated with the
effect. (eg: \cf{Withdraw 50}).  Since causally consistent operations require an
up-to-date view of the current session, the shim layer node synchronously
fetches operations if the causally preceding operations in the current
session are not available in its cache.  Strongly consistent operations are
performed after obtaining exclusive leases on objects. The lease mechanism
is implemented with the help of Cassandra's support for conditional updates
and expiring columns.

>>>>

Every generated effect on an object inserts a new row
$(o,e,\mathit{vis},\mathit{txn},\mathit{val})$ into the backing store, where
$o$ and $e$ are object and (unique) effect identifiers, \emph{vis} is the
set of effect identifiers visible to this operation, \emph{txn} is an
optional transaction identifier, and \emph{val} is the value associated with the
effect. (eg: \cf{Withdraw 50}).  Since causally consistent operations require an
up-to-date view of the current session, the shim layer node synchronously
fetches operations if the causally preceding operations in the current
session are not available in its cache.  Strongly consistent operations are
performed after obtaining exclusive leases on objects. The lease mechanism
is implemented with the help of Cassandra's support for conditional updates
and expiring columns.
